Approximation as Differentiation notes

### 2025-02-19 notes/definitions.tex
Some attempt to make sense of Grothendieck construction when F is contravariant.

\noindent Equivalently $\Fam(I,C)$ is the functor category $\Func{I}{C}$ where we interpret $I$ as a discrete
category. $\Fam(-,C): \Set^{\op} \to \Cat$ is the functor which sends any set $I$ to $\Fam(I,C)$ and any
function $f: I \to J$ to the following \emph{reindexing functor}.

@@

The Grothendieck construction for a functor $F: D \to \Cat$ is the category where:
\begin{itemize}
\item objects are pairs $(I, X)$ of an object $I$ of $D$ and an object of $FI$;
\item morphisms from $(I, X)$ to $(J, Y)$ are morphisms $f: I \to J$ in $D$ paired with a morphism $(Ff)(X) \to Y$ in $FJ$.
\end{itemize}

\noindent The fibred category $\Fam(C)$ over $\Set$ is the Grothendieck construction for the functor
$\Fam(-,C): \Set^{\op} \to \Cat$:
\begin{itemize}
\item objects are pairs $(I, X)$ of a set $I$ and indexed family $X$ in $\Fam(I,C)$;
\item morphisms from $(I, X)$ to $(J, Y)$ are functions $f: I \to J$ paired with a morphism $X \to Y[f]$ in
$\Fam(I,C)$.
\end{itemize}

>>>>

\noindent Equivalently $\Fam(I,C)$ is the functor category $\Func{I}{C}$ where we interpret $I$ as a discrete
category. $\Fam(-,C): \Set^{\op} \to \Cat$ is then the functor which sends any set $I$ to $\Fam(I,C)$ and any
function $f: I \to J$ to the following \emph{reindexing functor}.

@@

The \emph{Grothendieck construction} $\Grothendieck{D}F$ for a functor $F: D \to \Cat$ is the category where:
\begin{itemize}
\item objects are pairs $(I, X)$ of an object $I$ of $D$ and an object $X$ of $FI$;
\item morphisms from $(I, X)$ to $(J, Y)$ are morphisms $f: I \to J$ in $D$ paired with a morphism $(Ff)X
\to Y$ in $FJ$.
\end{itemize}

\noindent When $F$ is contravariant, a morphism from $(I, X)$ to $(J, Y)$ is a morphism $f: I \to J$ in $D$
paired with a morphism $X \to (Ff)Y$ in $FI$. Writing $\Fam(C)$ for the Grothendieck construction
$\Grothendieck{\Set^{\op}}\Fam(-,C)$ we then have that in $\Fam(C)$:
\begin{itemize}
\item objects are pairs $(I, X)$ of a set $I$ and indexed family $X$ in $\Fam(I,C)$;
\item morphisms from $(I, X)$ to $(J, Y)$ are functions $f: I \to J$ paired with a morphism $X \to Y[f]$ in
$\Fam(I,C)$.
\end{itemize}
